MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-08 paper.Rmd
Added subscripts.

| Matrix      | rows x columns     | Name                           | Description                                              |
|:------------|:-------------------|:-------------------------------|:---------------------------------------------------------|
| **R**       | industry x product | Resource matrix                | Contains exogeneous energy inputs to an ECC              |
| **U**       | product x industry | Use matrix                     | Describes how each energy conversion device uses energy; the sum of **U_feed** and **U_EIOU** |
| **U_feed**  | product x industry | Feedstock use matrix           | Describes feedstock inputs to energy conversion devices  |
| **U_EIOU**  | product x industry | Energy industry own use matrix | Describes how the energy industry uses energy            |
| **V**       | industry x product | Make matrix                    | Describes how each energy conversion device makes energy |
| **Y**       | product x industry | Final demand matrix            | Describes how each energy carrier is consumed            |

>>>>

| Matrix        | rows x columns     | Name                           | Description                                              |
|:--------------|:-------------------|:-------------------------------|:---------------------------------------------------------|
| **R**         | industry x product | Resource matrix                | Contains exogeneous energy inputs to an ECC              |
| **U**         | product x industry | Use matrix                     | Describes how each energy conversion device uses energy; the sum of **U**~feed~ and **U**~EIOU~ |
| **U**~feed~   | product x industry | Feedstock use matrix           | Describes feedstock inputs to energy conversion devices  |
| **U**~EOIU~   | product x industry | Energy industry own use matrix | Describes how the energy industry uses energy            |
| **V**         | industry x product | Make matrix                    | Describes how each energy conversion device makes energy |
| **Y**         | product x industry | Final demand matrix            | Describes how each energy carrier is consumed            |
